On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-04 AvdMomZvol_rails/Article.tex
[AMZr] Edits from Dr. Usachev - page 2

@@

\begin{theorem}
	Let $\mathcal{P}$ be a planar integral point set consisting of
	$n - 2$ points on the line $l_1$ and two points $P_{1}$ and $P_{2}$ on a
	parallel line $l_2$ with distance $r$ between $l_{1}$ and $l_{2}$. If there
	exist positive integers $v$, $w$ with $f^{2} + v^{2}
	= w^{2}$ and $v < 2r$, where $|P_{1}P_{2}| = f$,
	then

@@

First, we discuss the classification of planar integral points sets;
then, we present some bounds for $d(m,n)$ based on planar integral point sets of special types
and provide some general constructions of such bounds.

@@

\begin{dfn}
	A planar integral point sets of $n$ points with $n-1$ points on a straight line is called
	a \textit{facher} set.
\end{dfn}
Facher sets are very dominating examples of planar integral point sets.
In~\cite{antonov2008maximal}, facher sets with characteristic 1 are called \textit{semi-crabs}.
For $9 \leq n \leq 122$, the diameter $d(2,n)$ is reached on a facher point set~\cite{kurz2008minimum}.

For non-facher integral point sets situated in two straight lines,
we can easily distinct the following three cases:

@@

Among the rails sets, sets with 2 points on one line and all the other on another line dominate.

@@

Circular sets are very important examples
of integral point sets~\cite{harborth1993upper,piepmeyer1996maximum,bat2018number}.

@@

These six classes dominate among all the known planar integral point sets;
however, some sophisticated constructions are also known.

@@

Below $f$ and $w$ are those from Theorem~\ref{thm:rails_blowup}.

>>>>

\begin{dfn}
	The characteristic of a PIPS $\mathcal{P}$ is a squarefree number $q$
	such that the area of any triangle $M_1M_2M_3$, $\{M_1,M_2,M_3\}\subset \mathcal{P}$,
	is commensurable with $\sqrt{q}$.
\end{dfn}

@@

\begin{theorem}
	\label{thm:Kurz_blowup}
	Let $\mathcal{P}$ be a planar integral point set consisting of
	$n - 2$ points on the line $l_1$ and two points $P_{1}$ and $P_{2}$ on a
	parallel line $l_2$ with distance $r$ between $l_{1}$ and $l_{2}$. If there
	exist positive integers $v$, $w$ with $f^{2} + v^{2}
	= w^{2}$ and $v < 2r$, where $|P_{1}P_{2}| = f$,
	then

@@

In this paper we further study the various features of IPS.
In Section 2, we discuss the classification of planar integral points sets;
in Section 3, we present some bounds for $d(m,n)$ based on planar integral point sets of special types
and provide some general constructions of such bounds.

@@

\begin{dfn}
	A planar integral point sets of $n$ points with $n-1$ points on a straight line is called
	a \textit{facher} set.
\end{dfn}
Most of the examples of planar integral point sets turns to be facher sets.
In~\cite{antonov2008maximal}, facher sets with characteristic 1 are called \textit{semi-crabs}.
For $9 \leq n \leq 122$, the diameter $d(2,n)$ is attained on a facher point set~\cite{kurz2008minimum}.

Non-facher integral point sets situated in two straight lines
can be further classificated in the following three cases:

@@

Among the rails sets, sets with 2 points on one line and all the other on another line prevail.

@@

Circular sets are very important examples
of integral point sets~\cite{harborth1993upper,piepmeyer1996maximum,bat2018number};
for example, the best known upper bound for $d(2,n)$
is attained on a circular set.

@@

Most of the known planar integral point sets fall into these six classes;
however, there are some sophisticated examples which do not~\cite{kreisel2008heptagon,kurz2013constructing,avdeev2021particular}.
A lower bound for the diameter of a PIPS with no collinear triples (so-called PIPS \textit{in semi-general position})
is presented in~\cite{my-semi-general-5-4-bound-2019}.

@@

Below $f$ and $w$ are those from Theorem~\ref{thm:Kurz_blowup}.
